\newpage
\begin{rSection}{Selected Awards and Honors}
\begin{tabbing}
\hspace{3.6in}\= \hspace{2.1in}\= \kill
Best Paper Honorable Mention Award \> ICLAD \> 2025 \\
Jack and Mildred Bowers Scholarship \> CMU \> 2025 \\
Qualcomm Innovation Fellowship \> Qualcomm Inc. \> 2024 \\
Apple PhD fellowship in Integrated Systems \> Apple Inc. \> 2024 \\
Apple PhD fellowship in Integrated Systems \> Apple Inc. \> 2022 \\
Faculty Outstanding Thesis Award \> Engineering Faculty, CUHK \> 2021 \\
Dean's Fellowship \> CMU \> 2021 \\
Talent Development Scholarship \> HKSAR Goverment \> 2021 \\
Best Paper Award                       \> ASP-DAC                      \> 2021 \\
1st Place Award in EDA elite challenge\> Chinese Institute of Electronics \>2020 \\
Richard Newton Young Student Fellow    \> DAC \> 2020 \\
Best Student Paper Award                       \> ICTAI                      \> 2019 \\
Distinguished Paper Award                      \>ISSTA                     \>2019 \\
Full Postgraduate Studentship   \>CUHK  \>2019-2021\\
     2nd Place Award in CAD Contest               \> ICCAD                      \> 2018 \\
    ELITE Stream Student Scholarship                \> Faculty of Engineering, CUHK                       \> 2018      \\
    Undergraduate Admission Scholarship                             \> Soong Ching Ling Foundation  \> 2015-2018 \\
    % Dean’s List          \> Faculty of Engineering, CUHK                       \> 2015,2017,2018 \\
    % Best Undergraduate Summer Project Award \> Faculty of Engineering, CUHK            \> 2017\\
    % Head’s List          \> Chung Chi College, CUHK  \> 2015 \\
\end{tabbing}
\end{rSection}


\begin{rSection}{Patents}
    % \textbf{Preprint}
    % \begin{description}[font=\normalfont]
    % %{{{


        % \item[{[C10]}]{
        %     \textbf{Wei Li}, Ruxuan Li, Yuzhe Ma, Siu On Chan, Bei Yu, David
        %     ``Rethinking Graph Neural Networks for Graph Coloring Problem'', submitted to Innovative Applications of Artificial Intelligence Conference (AAAI) 2022, under review.
        % }
        % \item[{[C10]}]{
        %     \textbf{Wei Li}, Siu On Chan, Bei Yu,
        %     ``What is a global Graph Neural Network?'', submitted to International Conference on Computer Vision (ICCV) 2021, under review.
        % }
    % \end{description}
    \begin{description}[font=\normalfont]
    %{{{
        \item[{[p2]}]{
            \textbf{Wei Li}, Rongjian Liang, Haoxing Ren. ``Differentiable Global Router".
            U.S. Patent Application 18/965,415, Filed Dec 2, 2024.
            Assigned to NVIDIA Corp. - Patent Pending.
        }
        \item[{[P1]}]{
            \textbf{Wei Li}, Ronald Blanton, Jose M. F. Moura. ``System and Method for Global Floorplanning via Semidefinite Programming". U.S. Patent Application 18/910,938 (Filed: Oct 9, 2024) — Patent Pending.
        }
    \end{description}

\end{rSection}


