
\begin{rSection}{Teaching Experience}

    {\bf \textcolor{CUHKblue}{Carnegie Mellon University}}               \\
    {\bf {\textcolor{CUHKblue}{Head Teaching Assistant} \\ 18-765: Digital System Testing and Testable Design } \hfill{Fall 2025}}
    \begin{itemize}[noitemsep,topsep=-5pt]
        \item Curated and coordinated a guest seminar series featuring \textbf{10+ industry leaders} from \textbf{Apple, Broadcom, Qualcomm, Siemens, and Synopsys} to bridge theoretical testing concepts with industrial practices.
        \item Architected and implemented an \textbf{automated grading system}, ensuring consistent feedback for students.
        \item Led weekly office hours and technical Q\&A; coordinated the grading team to synchronize curriculum delivery.
    \end{itemize}
    {\bf {18-202: Mathematical Foundations of Electrical Engineering } \hfill{Spring 2023}}
    \begin{itemize}[noitemsep,topsep=-5pt]
        \item Conducted weekly recitations to simplify complex mathematical concepts for graduate students.
        \item Managed course logistics, grading, and student consultations. 
    \end{itemize}
    {\bf {\textcolor{CUHKblue}{Teaching Assistant} \\ 18-765: Digital System Testing and Testable Design }  \hfill{Fall 2022, Fall 2023, Fall 2024}}
    \begin{itemize}[noitemsep,topsep=-5pt]
        \item Developed and refined course assignments; provided in-depth technical support for projects.
    \end{itemize} 

{\bf \textcolor{CUHKblue}{The Chinese University of Hong Kong}}               \\
% \list{1}{2}
{\bf {\textcolor{CUHKblue}{Head Teaching Assistant} \\ CENG2030: Fundamentals of Embedded Systems }  \hfill{Spring 2021}}\\
{\bf { CENG3420: Computer Organization and Design }  \hfill{Spring 2020}}
\begin{itemize}[noitemsep,topsep=-5pt]
    \item Designed and supervised weekly laboratory tutorials, focusing on hardware-software co-design and system-level performance. \\
\end{itemize} 


\newpage
% \begin{tabbing}
%     \hspace{2in}\= \hspace{0.7in}\= \hspace{1in}\= \kill
% Spring 2020  \> CUHK  \>  CENG3420 \>Computer Organization and Design \\
% Spring 2021  \> CUHK  \>  CENG2030  \>Fundamentals of Embedded Systems \\
% Spring 2023 \> CMU \> 18202 \>Mathematical Foundations of Electrical Engineering \\
% Fall 2022,2023,2024,2025  \>  CMU \> 18765 \> Digital System Testing and Testable Design
%     %Silver Award in Student Research Contest    \> ACM                        \> 2013 \\
%     %MCD Fellowship                              \> UT Austin                  \> 2011-2012 \\
%     %Guanghua First Class Scholarship            \> Tsinghua University        \> 2009 \\
%     %Cadence Second Class Scholarship            \> Tsinghua University        \> 2009 
% \end{tabbing}
\end{rSection}



\begin{rSection}{Mentoring Experience}
    {\bf Undergraduate Students Mentored} 
    \vspace{-0.6em}
    \begin{tabbing}
        \hspace{1.5in}\= \hspace{1.5in}\= \hspace{1in}\= \kill

        Aug 2024 - Present \>  Yang Zou [C17, 18] \> CMU B.S. \> Stanford Ph.D. soon\\
        Aug 2019 - May 2020 \>  Yuxiao Qu [C8] \> CUHK B.S. \> CMU Ph.D. \\
        Aug 2019 - Dec 2019 \>  Jialu Li [C7] \> CUHK B.S. \> HKUST M.Phil. \\
        Aug 2019 - Dec 2019 \>  Jialu Xia [C7] \> CUHK B.S. \> Spring Labs. 
    \end{tabbing}
    {\bf Graduate Students Mentored} 
    \vspace{-0.6em}
    \begin{tabbing}
        \hspace{1.5in}\= \hspace{1.5in}\= \hspace{1in}\= \kill
        Sep 2025 - Present \>  Rebecca Dettmar \> CMU M.S. \> In progress \\
        Sep 2025 - Present \>  Zifeng Wang \> CMU M.S. \> In progress \\
        Sep 2025 - Present \>  Andrew Kim \> CMU M.S. \> In progress \\
        Sep 2025 - Jan 2026 \>  Yixin Liang [18] \> CMU M.S. \> NVIDIA 
    \end{tabbing}
    \end{rSection}
    
    \begin{rSection}{Professional Service}

        {\bf \textcolor{CUHKblue}{Journal \& Conference Reviewer}}               
        \begin{itemize}[noitemsep,topsep=-5pt]
            \item \textbf{Journals}: IEEE TCAD, IEEE TIFS, ACM TODAES, The ANZIAM Journal, Integration (the VLSI Journal).
            \item \textbf{Conferences} (Sub-reviewer/External): DAC, ITC, VTS, ETS.
        \end{itemize}
        {\bf \textcolor{CUHKblue}{Departmental Service}} \\
        {\bf {Student Representative (Volunteer), CMU ECE Faculty Search Committee} }              \hfill{2025} 
        \begin{itemize}[noitemsep,topsep=-5pt]
            \item Participated in candidate interviews and social evaluations for Tenure-Track Assistant Professor applicants; 
            \item Provided student-perspective feedback to the hiring committee.
        \end{itemize}
        {\bf {Volunteer, CMU ECE PhD Open House} }              \hfill{2025} 
        \begin{itemize}[noitemsep,topsep=-5pt]
            \item Mentored prospective PhD students and introduced research work;
        \end{itemize}
        {\bf {PhD Student Contact} }              \hfill{2026} 
        \begin{itemize}[noitemsep,topsep=-5pt]
            \item Provided insights to admitted PhD students about research and life at CMU; ßßß
            \item facilitated their transition into the program.
        \end{itemize}
\end{rSection}


\begin{rSection}{Selected Invited Talks}

    \begin{tabbing}
        \hspace{.7in}\= \hspace{4in}\=  \kill
        2026.02 \>  \textbf{Differentiable ATPG w. Mathematical Foundations} \> Apple  \\
        2026.01 \>  \textbf{Towards Autonomous EDA: Research and Vision} \> Ricursive Intelligence (Founding Team)  \\
        2025.08 \>  \textbf{When LLMs Meet Graphs} \> Apple  \\
        2025.01 \>  \textbf{Review on ATPG and Fault Modeling} \> NVIDIA Research  \\
        2024.11 \>  \textbf{Differentiable Global Routing} \> Apple  \\

    \end{tabbing}

\end{rSection}